A Multi-telescope Campaign on \frb: Implications for the FRB Population

### 2017-05-18 repeater-vladata.tex
added pwkit cite
working through jim comments. rescaled vla energies but vla limit seems off

\begin{abstract}
We present results of the coordinated observing campaign that made the first subarcsecond localization of a Fast Radio Burst, \frb. Of the nine bursts detected by the Very Large Array at 3~GHz, three had simultaneous observing coverage at other observatories. Only one VLA burst was detected by another observatory, the Arecibo Observatory at 1.4~GHz. We use multi-observatory constraints and modeling of bursts seen only at 3~GHz to confirm earlier results showing that burst spectra are not well characterized by a power law. We find that burst spectra are characterized by a $\sim500$~MHz envelope and apparent radio energy as high as $10^{40}$\ erg. We attribute significant changes in the apparent dispersion between bursts to frequency-dependent profiles that add a random error to the estimate of DM by up to 1\%. We use \frb\ as a prototype of the FRB class to estimate a volumetric birth rate of FRB sources $R_{\rm{FRB}} \approx 5\times10^{-5}/N_r$\ Mpc$^{-3}$\ yr$^{-1}$, where $N_r$\ is the number of bursts per source over its lifetime. This rate is broadly consistent with models of FRBs from young pulsars or magnetars born in superluminous supernovae or long gamma-ray bursts, if the typical FRB repeats on the order of $10^3$\ times during its lifetime.

@@

\includegraphics[width=2\columnwidth]{timeline.pdf}
\caption{The top and bottom panels summarize the observations and detections of \frb\ in the 2015 and 2016 campaigns. Circles highlight observations that detected bursts from \frb\ with multiple burst detections indicated with a heavy line. The black dashed lines show the VLA burst detections with simultaneous coverage at other telescopes and the solid line shows the simultaneous burst detection. Circled observations with no line indicate observations on the same day that did not overlap. Days with observations are indicated with radio band designations 4, L, S, C, U referring to radio frequencies of 70~MHz, 1.4, 3, 4.5, and 15~GHz, respectively.
\label{fig:sched}}
\end{center}
\end{figure*}

@@

All VLA fast-sampled data were observed with 5~ms sampling, 256 channels, and dual-circular polarization \citep{2015ApJ...807...16L}. The channel frequency width was set to maximize sensitivity to the known DM of \frb\ with the largest total bandwidth. The total bandwidths at L (1.4~GHz), S (3~GHz), and C (6~GHz) bands were 256~MHz, 1024~MHz, and 2048~MHz, respectively. The 3~GHz data were recorded data in eight spectral windows with 32 channels each and had sensitivity of 5~mJy in 5~ms ($1\sigma$).

@@

During the late-2016 campaign, Arecibo observed with the L-wide receiver using the PUPPI pulsar backend. The observational frequency range was 1.15 to 1.73~GHz and frequency resolution was 1.5625~MHz, which has a typical sensitivity of 2~mJy in 2~ms ($1\sigma$). We recorded total full Stokes polarization intensity spectra with a time resolution of 10.24~$\mu$s. Each frequency channel was coherently dedispersed to 557~pc cm$^{-3}$, significantly reducing intra-channel dispersion smearing. The full width at half maximum (FWHM) beam size at band center is 3.3\arcmin.

@@

We observed \frb\ with AMI-LA for 3 hours each on four epochs starting at MJDs 57638, 57643, 57645, 57646, 57648, and 57649. Observations were made with the new digital correlator having 4096 channels across a 5~GHz bandwidth between 13--18~GHz with a 1~s integration time. The phase calibrator, J0518+3306, was observed every 12 minutes for about 1.5 minutes. The AMI-LA data were binned to eight 0.625~GHz channels and processed (RFI excision and calibration) with a fully-automated pipeline, AMI-REDUCE \citep[e.g.,][]{2013MNRAS.429.3330P}. Daily measurements of 3C48 and 3C286 were used for the absolute flux calibration, which is good to about 10\%.

@@

Four of the VLA bursts had simultaneous observing coverage with either Arecibo, Effelsberg, or AMI-LA. Two of the VLA bursts had simultaneous observing coverage by all four observatories (Figure \ref{fig:sched}). Of these bursts, only one VLA burst (on MJD 57648) was simultaneously detected by another observatory (Arecibo).

Figure \ref{fig:sgram} shows a dynamic spectrum for this burst with both VLA and Arecibo data. The temporal resolution of the VLA data (5~ms) is much coarser than that of Arecibo, so data were resampled to the Arecibo temporal grid after correcting for barycentric and dispersion measure offsets. We assumed a DM of 560.5 pc cm$^{-3}$ (Hessels et al., in prep) to calculate a dispersion delay of 189 and 734~ms from infinite frequency to the top of the VLA and Arecibo bands, respectively. An error in the DM of 1 pc cm$^{-3}$\ corresponds to a delay time correction error of 0.3 and 1.4~ms for the VLA and Arecibo bands, respectively. We used PRESTO to calculate a relative barycentric time correction of 3.8~ms between the VLA and Arecibo at the time of observation.

@@

\begin{figure}[htb]
\begin{center}
 \includegraphics[trim=250 400 250 80, clip, width=\columnwidth]{aovla_spec.pdf}
 \caption{Composite dynamic specrum for the burst from \frb\ on MJD 57648 with data from the VLA and Arecibo observatories. The time axis is measured in milliseconds relative to MJD 57648.437788874842 with times corrected to the barycenter and infinite frequency (assuming DM$=560.5$\ pc $^{-3}$). The thick black line separates data from the VLA (2.5 to 3.5~GHz) and Arecibo (1.1 to 1.8~GHz) and flagged data are grey. The amplitude scale is normalized by assuming the Arecibo to VLA gain ratio is 10.
 \label{fig:sgram}}
\end{center}
\end{figure}

Figure \ref{fig:multi} shows coarse spectra built from integrated flux densities measured (or limited) for three bursts with multi-telescope observing coverage. The burst on MJD 57648 was detected with VLA and Arecibo with significances of 25$\sigma$\ and 39$\sigma$, which corresponds to peak flux densities in 5~ms of $111\pm5$\ mJy and $14\pm0.4$\ mJy at 3 and 1.4~GHz, respectively. The VLA observations underresolve the pulses in time, so to compare these values, we assume a typical pulse width of 2~ms. Under this assumption, the VLA and Arecibo integrated flux densities are $278\pm13$\ and $64\pm2$\ mJy at 3 and 1.4~GHz, respectively. Assuming a power law flux density model ($S_{\nu} \propto \nu^{\alpha}$), we find a spectral index $\alpha=1.9$. This is inconsistent with the spectral index limit implied by the Effelsberg nondetection at 4.5~GHz ($\alpha<-1.7$\ for a 2~ms burst and $5\sigma$ limit).

@@

\begin{figure}[htb]
\begin{center}
 \includegraphics[width=\columnwidth]{multispec.pdf}
 \caption{Broadband spectral measurements and limits for three bursts of \frb\ with simultaneous multi-telescope observing coverage. Upper limits assume a pulse width of 2~ms and a $5\sigma$ detection threshold. Measurements (dots) and limits (triangles) are shown for Arecibo, VLA, and Effelsberg at 1.4, 3, and 4.5~GHz, respectively; limits from LWA1 and AMI-LA are not visible on this scale. Errors in flux density are comparable to the symbol size and are not shown. Overlapping points are offset by tens of MHz in frequency for clarity.
 \label{fig:multi}}
\end{center}
\end{figure}

\subsection{VLA Bursts}
\subsubsection{Spectral Modeling}
\label{sec:spec}

@@

Table \ref{tab:spec} summarizes the properties of all nine VLA bursts. Parameters such as integrated flux density, S/N, and Stokes V were measured from the burst properties integrated in frequency. Stokes V values estimated from the dual-circular feeds as $(RR-LL)/(RR+LL)\approx3\%$, which is comparble to the systematic error induced by the primary beam\footnote{See EVLA memo \#195 at \url{https://library.nrao.edu/public/memos/evla/EVLAM_195.pdf}.}. Given that systematic effects dominate the apparent circular polarization, this observation limits the fractional circular polarization to less than 3\%.

\begin{table*}
\caption{Properties of \frb\ Bursts Seen by VLA at 3~GHz}
%\centering
\begin{tabular}{cc|rrr|ccrrrr}
\multicolumn{2}{c|}{Time} & \multicolumn{3}{c|}{Observed properties} & \multicolumn{6}{c}{Modeled properties} \\ \hline
Calendar day & Burst time   & S/N & $S_{\rm{I, 5~ms}}$	& $S_{\rm{V}}$ 	& DM 			& W 			& $S_{\rm{I,peak}}$ & Center & FWHM & $E_{\rm{int}}$ \\
(2016)       &  (MJD)     &   (image)    & (mJy) 			& (mJy) 		    & (pc cm$^{-3})$ 	& (ms) 			& (mJy) 			& (GHz)  & (MHz) & ($10^{38}$\ erg)\\ \hline
23 Aug & 57623.74402686      & 38 		& 194			& +3				& 567$\pm2$ 		& 2.0$\pm0.2$	 		& 690 		& 2.8 		& 290 & 11 			\\
2 Sep & 57633.67986367      & 179 		& 1500			& --35 				& 568.2$\pm0.2$ 	& 2.05$\pm0.02$			& 3340 		& 3.2 		& 510 & 98				\\
2 Sep\tablenotemark{c} & 57633.69515938 & 15 & 69		& +2				& 562$^{+4}_{-6}$ 	& 2.5$^{+0.9}_{-0.6}$	& $>$430 	& $<$2.5	& $<$290 & 7  			\\
7 Sep & 57638.49937435      & 12 		& 55			& +5 				& 567$^{+7}_{-9}$ 	& 1.3$^{+1.4}_{-0.8}$	& 130 		& 3.1 		& 420 & 3  			\\
12 Sep\tablenotemark{a} & 57643.45730263  & 100 		& 508 & --5 		& 565.6$^{+0.6}_{-0.5}$ & 1.9$\pm0.1$		& 1170 		& 2.8 		& 510 & 34 			\\
14 Sep\tablenotemark{a} & 57645.42958602   & 13 		& 64 & +3			& 563$^{+5}_{-4}$ 	& 1.1$\pm0.7$		 	& 170 		& 2.8 		& 380 & 4  			\\
15 Sep\tablenotemark{c} & 57646.46600650 & 20 & 87		& +1				& 569$\pm5$ 		& 2.5$^{+0.9}_{-1.4}$	& $>$420 	& $<$2.5 	& $<$430 & 10 			\\	
17 Sep\tablenotemark{a,b} & 57648.43691490 & 25 & 111	& +9				& 564$\pm2$ 		& 1.4$^{+0.3}_{-0.4}$	& 260 		& 2.8 		& 470 & 7  			\\
18 Sep\tablenotemark{a} & 57649.45175697   & 36 		& 167 & +1			& 567$\pm2$ 		& 2.1$\pm0.5$		 	& 290 		& 3.0 		& 690 & 12 			\\ \hline
\end{tabular}
\tablecomments{$S_{\rm{V}}$ is the measured circular polarization of the burst, which dominated by systematic effects. All error ranges represent 68\% confidence intervals.}
\tablenotetext{a}{Simultaneously observed by either Arecibo, Effelsberg, LWA1, or AMI-LA.}
\tablenotetext{b}{Detected simultaneously with Arecibo.}
\tablenotetext{c}{Best-fit Gaussian is not centered in 3~GHz band, so spectral parameters are limits.}
\label{tab:spec}
\end{table*}

@@

We used a Markov chain Monte Carlo (MCMC) method to model the dynamic radio spectra (time versus frequency). We used the Goodman and Weare affine invariant sampler \citep{goodman2010ensemble} as implemented in \emph{emcee} \citep{2013PASP..125..306F}. The dynamic spectra were modeled prior to dispersion correction. The spectral structure was modeled as a broad Gaussian envelope (parameters of amplitude, center, $\sigma$), while the time evolution was modeled by a $\nu^2$\ dispersion law (parameters of starting integration, DM). Finally, the pulses were assumed to have an intrinsically square temporal width (parameter W). This 6-parameter model defined the intrinsic signal that was then distributed over a fixed time-frequency observing grid. The inter-channel amplitude modulation was ignored in the model.

@@

% ** signal or noise analysis offered by jim **

@@

 \begin{minipage}{2\columnwidth}
  \includegraphics[width=0.5\columnwidth]{spec_57649.pdf}
 \end{minipage}
\caption{Spectra and best-fit model for nine bursts seen by the VLA from 2.5 to 3.5~GHz in the peak, dedispersed 5~ms integration. The solid line is a best-fit Gaussian model found through modeling. The typical flux density error per channel is 70~mJy, which is shown at the top right of each panel next to the MJD label.
\label{fig:spec}}
\end{center}
\end{figure*}

This analysis differs from traditional analysis in that it simultaneously models the spectral and temporal evolution of the burst. A typical \frb\ burst takes $\sim180$~ms or 36 integrations to cross the observing band from 2.5 to 3.5~GHz. The effect of a finite pulse width is visible as the burst moves from one integration to the next, even for widths narrower than the integration time of 5~ms. Table \ref{tab:spec} shows that the typical burst width is measured as $2\pm0.5$~ms (68\% confidence interval); the inter-channel dispersion smearing ranges from 0.4 to 1.1~ms across this band. The brightest burst (on 57633.68) is modeled with a temporal width of $2.05\pm0.02$~ms and its arrival time is measured with a precision of $\sim50~\mu$s. Note that these errors are only accurate to the degree that the model represents the data. One potential bias in the model is that we do not model scintillation effects.

@@

The initial VLA detections were made with a matched-filter approach that allowed inter-DM sensitivity losses up to roughly 10\% \citep[$\Delta \rm{DM}=10\ \rm{pc}\ \rm{cm}^{-3}$][]{2003ApJ...596.1142C}. The MCMC modeling is more sophisticated in that it considers a wider range of parameters and models both data and observing effects (frequency-time pixel boundaries) simultaneously.

Figure \ref{fig:dmdt} compares the 68\% confidence intervals on the DM for all nine VLA bursts against detection time (top panel) and the modeled burst temporal width (bottom panel). The error weighted mean burst DM is 567.8$\pm$0.1 pc cm$^{-3}$, significantly larger than the long-term average of 560.5 pc cm$^{-3}$ seen by Arecibo during this campaign. However, we note that the 95\% confidence intervals in DM for multiple bursts are not consistent with this mean nor each other, which suggests that some burst-specific property can bias the measured DM. The variation in DM observed by the VLA at 3~GHz is similar to that reported for Arecibo observations of \frb\ in \citet{2016arXiv160308880S}.
% This is consistent with the idea that the DM measured at low temporal resolution (e.g., by the VLA or by single-dish observatories without coherent dedispersion) is determined by extrinsic (an electron column) dispersion and some spectrotemporal structure that changes between bursts.

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=\columnwidth]{burst_dmdt.pdf}
\caption{(Top) Burst time versus DM for nine 3~GHz bursts detected by the VLA. The DM scale for both panels is shown at the bottom. The 68\% confidence interval on DM is shown with a bar and the dashed line shows the best-fit DM$=560.5$\ pc cm$^{-3}$ inferred from Arecibo observations at 1.4~GHz (Hessels et al, in prep). (Bottom) Temporal width versus burst DM for the same nine VLA bursts.
\label{fig:dmdt}}
\end{center}
\end{figure}

\subsection{Temporal Statistics}
\label{sec:temp}

The burst rate for \frb\ varied dramatically throughout the 2016 observing campaign (Figure \ref{fig:sched}). In the early-2016 campaign, we observed for 30 hours at 3~GHz and no bursts were detected. In the late-2016 observing campaign, we observed for 27 hours at 3~GHz and detected nine bursts. Overall, the data quality is uniform and high, so the inhomogeneous burst distribution shows that the burst rate was not uniform.

@@

\subsection{Energy and Brightness Distribution}
\label{sec:disn}

Knowing the source distance, we calculate the burst energy by integrating flux in time and frequency (Table \ref{tab:spec}). Some VLA burst spectra seem to be contained by the 2.5 to 3.5~GHz band and most of them seem to have Gaussian envelopes that are well modeled by the emission within that band. Assuming that the Gaussian shape defines the full emission window, the mean 3~GHz flux density can be converted to a total energy with no further assumptions about the burst spectral properties.

@@

Broadly, the range of energies shown in Figure \ref{fig:ed} is defined by the sensitivity of the telescope and the duration of the observing campaign. The VLA distribution shown represents the 27-hour, late-2016 campaign, which is longer than the single-dish campaigns presented here. However, since the VLA observations have a relatively coarse time resolution, it is not as sensitive as Arecibo and the GBT, so no bursts with energiest less than $3\times10^{38}$~erg were detected. The rate upper limit (95\% confidence) from the early-2016 VLA campaign shows that even identical observing campaigns have different detection rates.

We modeled the differential energy distribution, $dN/d\log{E}$, again using a Poisson detection probability with a rate function $\lambda = A E^{\alpha}$. Rather than trying to estimate a completeness limit for each energy distribution, we assume an effective detection limit of 0.9 times the weakest burst detected; the best-fit slope is weakly dependent on this, but general conclusions are robust. We directly sampled the likelihood distribution to estimate a best slope of $\alpha_{\rm{VLA}}=-0.7^{+0.3}_{-0.4}$, $\alpha_{\rm{Arecibo}}=-0.8^{+0.3}_{-0.5}$, and $\alpha_{\rm{GBT}}=-0.8^{+0.4}_{-0.5}$ (68\% confidence interval). Expressed as a power law function in $dN/dE$, the slope index is approximately --1.7.

@@

@@

\software{\emph{rtpipe}, \emph{realfast}}

>>>>

\begin{abstract}
We present results of the coordinated observing campaign that made the first subarcsecond localization of a Fast Radio Burst, \frb. During this campaign, we made the first detection of an FRB burst by multiple telescopes: the VLA at 3~GHz and the Arecibo Observatory at 1.4~GHz. Of the nine bursts detected by the Very Large Array at 3~GHz, four had simultaneous observing coverage at other observatories. 
We use multi-observatory constraints and modeling of bursts seen only at 3~GHz to confirm earlier results showing that burst spectra are not well characterized by a power law. We find that burst spectra are characterized by a $\sim500$~MHz envelope and apparent radio energy as high as $10^{40}$\ erg. We measure significant changes in the apparent dispersion between bursts that can be attributed to frequency-dependent profiles or some other intrinsic burst structure that adds a random error to the estimate of DM by up to 1\%. We use \frb\ as a prototype of the FRB class to estimate a volumetric birth rate of FRB sources $R_{\rm{FRB}} \approx 5\times10^{-5}/N_r$\ Mpc$^{-3}$\ yr$^{-1}$, where $N_r$\ is the number of bursts per source over its lifetime. This rate is broadly consistent with models of FRBs from young pulsars or magnetars born in superluminous supernovae or long gamma-ray bursts, if the typical FRB repeats on the order of $10^3$\ times during its lifetime.

@@

\includegraphics[width=2\columnwidth]{timeline.pdf}
\caption{The top and bottom panels summarize the observations and detections of \frb\ in the 2015 and 2016 campaigns. Circles highlight observations that detected bursts from \frb\ with multiple burst detections indicated with a heavy line. The black dashed lines show the VLA burst detections with simultaneous coverage at other telescopes and the solid line shows the simultaneous burst detection. Circled observations with no line indicate bursts that did not have simultaneous observing coverage at the VLA. Days with observations are indicated with radio band designations 4, L, S, C, U referring to radio frequencies of 70~MHz, 1.4, 3, 4.5, and 15~GHz, respectively.
\label{fig:sched}}
\end{center}
\end{figure*}

@@

All VLA fast-sampled data were observed with 5~ms sampling, 256 channels, and dual-circular polarization \citep{2015ApJ...807...16L}. The total bandwidths at L (1.4~GHz), S (3~GHz), and C (6~GHz) bands were 256, 1024, and 2048~MHz, respectively, corresponding to channel bandwidths of  1, 4, and 8~MHz. The dispersion smearing across a channel is $\sim1.7$, 0.7, and 0.2~ms in the same respective bands. The 3~GHz data were recorded data in eight spectral windows with 32 channels each and had sensitivity of 5~mJy in 5~ms ($1\sigma$).

@@

Arecibo observed with the L-wide receiver using the PUPPI pulsar backend. The observational frequency range was 1.15 to 1.73~GHz and frequency resolution was 1.5625~MHz, which has a typical sensitivity of 2~mJy in 2~ms ($1\sigma$). We recorded total full Stokes polarization intensity spectra with a time resolution of 10.24~$\mu$s. Each frequency channel was coherently dedispersed to 557~pc cm$^{-3}$, significantly reducing intra-channel dispersion smearing. The full width at half maximum (FWHM) beam size at band center is 3.3\arcmin.

@@

We observed \frb\ with AMI-LA for 3 hours each on four epochs starting at MJDs 57638, 57643, 57645, 57646, 57648, and 57649. Observations were made with the new digital correlator having 4096 channels across a 5~GHz bandwidth between 13--18~GHz with a 1~s integration time. The phase calibrator, J0518+3306, was observed every 12 minutes for about 1.5 minutes. The AMI-LA data were binned to eight 0.625~GHz channels and processed (interference excision and calibration) with a fully-automated pipeline, AMI-REDUCE \citep[e.g.,][]{2013MNRAS.429.3330P}. Daily measurements of 3C48 and 3C286 were used for the absolute flux calibration, which is good to about 10\%.

@@

Figure \ref{fig:sgram} shows a dynamic spectrum for the first FRB burst to be detected simultaneously at two telescopes. This burst, on MJD 57648, was detected both by the VLA and Arecibo while upper limits were measured by simultaneous observations at the other three telescopes. In total, four of the VLA bursts had simultaneous observing coverage with either Arecibo, Effelsberg, LWA1, or AMI-LA. Two of the VLA bursts had simultaneous observing coverage by all four observatories, including the burst detected by Arecibo (Figure \ref{fig:sched}).

To generate the multi-telescope dynamic spectrum, the VLA data were resampled to the Arecibo temporal grid after correcting for barycentric and dispersion measure offsets. We assumed a DM of 560.5 pc cm$^{-3}$ (Hessels et al., in prep) to calculate a dispersion delay of 189 and 734~ms from infinite frequency to the top of the VLA and Arecibo bands, respectively. An error in the DM of 1 pc cm$^{-3}$\ corresponds to a delay time correction error of 0.3 and 1.4~ms for the VLA and Arecibo bands, respectively. We used PRESTO to calculate a relative barycentric time correction of 3.8~ms between the VLA and Arecibo at the time of observation.

@@

\begin{figure}[htb]
\begin{center}
 \includegraphics[trim=250 400 250 80, clip, width=\columnwidth]{aovla_spec.pdf}
 \caption{Composite dynamic specrum for the burst from \frb\ on MJD 57648 with data from the VLA and Arecibo observatories. The time axis is measured in milliseconds relative to MJD 57648.437788874842 with times corrected to the barycenter and infinite frequency (assuming DM$=560.5$\ pc $^{-3}$). The thick black line separates data from the VLA (2.5 to 3.5~GHz) and Arecibo (1.1 to 1.8~GHz) and flagged data are grey. For clarity, the VLA and Arecibo data are independently normalized to units of S/N per pixel; Arecibo is 5 times more sensitive than the VLA.
 \label{fig:sgram}}
\end{center}
\end{figure}

Figure \ref{fig:multi} shows coarse spectra built from integrated flux densities measured (or limited) for the three VLA bursts with observing coverage by Arecibo or Effelsberg. The burst on MJD 57648 was detected with VLA and Arecibo with significances of 25$\sigma$\ and 39$\sigma$, which corresponds to peak flux densities in 5~ms of $111\pm5$\ mJy and $14\pm0.4$\ mJy at 3 and 1.4~GHz, respectively. The VLA observations underresolve the pulses in time, so to compare these values, we assume a typical pulse width of 2~ms. Under this assumption, the VLA and Arecibo integrated flux densities are $278\pm13$\ and $64\pm2$\ mJy at 3 and 1.4~GHz, respectively. Assuming a power law flux density model ($S_{\nu} \propto \nu^{\alpha}$), we find a spectral index $\alpha=1.9$. This is inconsistent with the spectral index limit implied by the Effelsberg nondetection at 4.5~GHz ($\alpha<-1.7$\ for a 2~ms burst and $5\sigma$ limit).

@@

\begin{figure}[htb]
\begin{center}
 \includegraphics[width=\columnwidth]{multispec.pdf}
 \caption{Broadband spectral measurements and limits for three bursts of \frb\ with observing coverage by Arecibo or Effelsberg. Upper limits assume a pulse width of 2~ms and a $5\sigma$ detection threshold. Measurements (dots) and limits (triangles) are shown for Arecibo, VLA, and Effelsberg at 1.4, 3, and 4.5~GHz, respectively; limits from LWA1 and AMI-LA are not visible on this scale. Errors in flux density are comparable to the symbol size and are not shown. Overlapping points are offset by tens of MHz in frequency for clarity.
 \label{fig:multi}}
\end{center}
\end{figure}

\subsection{VLA Bursts}

\subsubsection{Spectrotemporal Modeling}
\label{sec:spec}

@@

Table \ref{tab:spec} summarizes the spectrotemporal properties of all nine VLA bursts. Parameters such as integrated flux density, S/N, and Stokes V were measured from the burst properties integrated in frequency. Stokes V values were estimated from the dual-circular feeds as $(RR-LL)/(RR+LL)\approx3\%$, which is comparble to the systematic error expected from beam squint at this location in the primary beam \footnote{See EVLA memo \#195 at \url{https://library.nrao.edu/public/memos/evla/EVLAM_195.pdf}.}. Given that systematic effects dominate the apparent circular polarization, this observation limits the fractional circular polarization to less than 3\%.

\begin{table*}
\caption{Properties of \frb\ Bursts Seen by VLA at 3~GHz}
%\centering
\begin{tabular}{cc|rrr|ccrrrr}
\multicolumn{2}{c|}{Time} & \multicolumn{3}{c|}{Observed properties} & \multicolumn{6}{c}{Modeled properties} \\ \hline
Calendar day & Burst time   & S/N & $S_{\rm{I, 5~ms}}$	& $S_{\rm{V}}$ 	& DM 			& W 			& $S_{\rm{I,peak}}$ & Center & FWHM & $E_{\rm{int}}$ \\
(2016)       &  (MJD)     &   (image)    & (mJy) 			& (mJy) 		    & (pc cm$^{-3})$ 	& (ms) 			& (mJy) 			& (GHz)  & (MHz) & ($10^{38}$\ erg)\\ \hline
23 Aug & 57623.74402686      & 38 		& 194			& +3				& 567$\pm2$ 		& 2.0$\pm0.2$	 		& 690 		& 2.8 		& 290 & 4.6 	\\
2 Sep & 57633.67986367      & 179 		& 1500			& --35 				& 568.2$\pm0.2$ 	& 2.05$\pm0.02$			& 3340 		& 3.2 		& 510 & 40		\\
2 Sep\tablenotemark{c} & 57633.69515938 & 15 & 69		& +2				& 562$^{+4}_{-6}$ 	& 2.5$^{+0.9}_{-0.6}$	& $>$430 	& $<$2.5	& $<$290 & 3.6 	\\
7 Sep & 57638.49937435      & 12 		& 55			& +5 				& 567$^{+7}_{-9}$ 	& 1.3$^{+1.4}_{-0.8}$	& 130 		& 3.1 		& 420 & 0.8  	\\
12 Sep\tablenotemark{a} & 57643.45730263  & 100 		& 508 & --5 		& 565.6$^{+0.6}_{-0.5}$ & 1.9$\pm0.1$		& 1170 		& 2.8 		& 510 & 13 		\\
14 Sep\tablenotemark{a} & 57645.42958602   & 13 		& 64 & +3			& 563$^{+5}_{-4}$ 	& 1.1$\pm0.7$		 	& 170 		& 2.8 		& 380 & 0.8  	\\
15 Sep\tablenotemark{c} & 57646.46600650 & 20 & 87		& +1				& 569$\pm5$ 		& 2.5$^{+0.9}_{-1.4}$	& $>$420 	& $<$2.5 	& $<$430 & 5.0 	\\	
17 Sep\tablenotemark{a,b} & 57648.43691490 & 25 & 111	& +9				& 564$\pm2$ 		& 1.4$^{+0.3}_{-0.4}$	& 260 		& 2.8 		& 470 & 2.0  	\\
18 Sep\tablenotemark{a} & 57649.45175697   & 36 		& 167 & +1			& 567$\pm2$ 		& 2.1$\pm0.5$		 	& 290 		& 3.0 		& 690 & 4.9 	\\ \hline
\end{tabular}
\tablecomments{$S_{\rm{V}}$ is the measured circular polarization of the burst, which dominated by systematic effects. All error ranges represent 68\% confidence intervals.}
\tablenotetext{a}{Simultaneously observed by either Arecibo, Effelsberg, LWA1, or AMI-LA.}
\tablenotetext{b}{Detected simultaneously with Arecibo.}
\tablenotetext{c}{Best-fit Gaussian is not centered in 3~GHz band, so spectral parameters are limits.}
\label{tab:spec}
\end{table*}

@@

We used a Markov chain Monte Carlo (MCMC) method to model the dynamic radio spectra (time versus frequency). We used the Goodman and Weare affine invariant sampler \citep{goodman2010ensemble} as implemented in \emph{emcee} \citep{2013PASP..125..306F}. The dynamic spectra were modeled prior to dispersion correction. The spectral structure was modeled as a broad Gaussian envelope (parameters of amplitude, center, $\sigma$), while the time evolution was modeled by a $\nu^2$\ dispersion law (parameters of starting integration, DM). Finally, the pulses were assumed to have an intrinsically square temporal width (parameter W). This 6-parameter model defined the intrinsic signal that was then distributed over a fixed time-frequency observing grid.

@@

@@

 \begin{minipage}{2\columnwidth}
  \includegraphics[width=0.5\columnwidth]{spec_57649.pdf}
  \includegraphics[width=0.5\columnwidth]{specAO_57648.pdf}
 \end{minipage}
\caption{Ten panels show spectra for nine VLA bursts and one Arecibo burst (bottom right). The VLA spectra are drawn from flux-calibrated, dedispersed 5~ms integrations. The Arecibo spectrum is drawn from a 2.7~ms window with 3.125~MHz channels and the flux scale is esimated using the radiometer equation. The solid line shown with VLA spectra is a best-fit Gaussian model found through modeling. The typical VLA flux density error per channel is 70~mJy, which is shown at the top right of each panel next to the MJD label.
\label{fig:spec}}
\end{center}
\end{figure*}

Our approach simultaneously models the spectral and temporal evolution of the burst. A typical \frb\ burst takes $\sim180$~ms or 36 integrations to cross the observing band from 2.5 to 3.5~GHz. The effect of a finite pulse width is visible as the burst moves from one integration to the next, even for widths narrower than the integration time of 5~ms. Table \ref{tab:spec} shows that the typical burst width is measured as $2\pm0.5$~ms (68\% confidence interval); the inter-channel dispersion smearing ranges from 0.4 to 1.1~ms across this band. The brightest burst (on MJD 57633.68) is modeled with a temporal width of $2.05\pm0.02$~ms and its arrival time is measured with a precision of $\sim50~\mu$s. Note that these errors are only accurate to the degree that the model represents the data. One potential bias in the model is that we do not model scintillation effects.

@@

The spectrotemporal modeling presented in \S \ref{sec:spec} provides marginalized posterior distributions for burst DM and pulse width. Figure \ref{fig:dmdt} compares the 68\% confidence intervals on the DM for all nine VLA bursts against detection time (top panel) and the modeled burst temporal width (bottom panel). The error weighted mean burst DM is 567.8$\pm$0.1 pc cm$^{-3}$, significantly larger than the long-term average of 560.5 pc cm$^{-3}$ seen by Arecibo during this campaign. Furthermore, several of the 95\% confidence intervals in DM are not consistent with this mean nor each other, which suggests that some burst-specific property can bias the measured DM. The variation in DM observed by the VLA at 3~GHz is similar to that reported for Arecibo observations of \frb\ in \citet{2016arXiv160308880S}.

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=\columnwidth]{burst_dmdt.pdf}
\caption{(Top) Burst epoch versus DM for nine 3~GHz bursts detected by the VLA. The DM scale for both panels is shown at the bottom. The 68\% confidence interval on DM is shown with a bar and the dashed line shows the best-fit DM$=560.5$\ pc cm$^{-3}$ inferred from Arecibo observations at 1.4~GHz (Hessels et al, in prep). (Bottom) Temporal width versus burst DM for the same nine VLA bursts.
\label{fig:dmdt}}
\end{center}
\end{figure}

\subsubsection{Fine Spectral Structure}

The spectral fits in Figure \ref{fig:spec} have residuals that include single samples that deviate by many standard deviations, particularly in the bursts on MJDs 57623,  57633.6, and 57643. These do not appear to be caused by terrestrial interference. They are most likely spectral variations from diffractive interstellar scintillations that, as noted previously, have characteristic frequency widths slightly larger than the 4~MHz channel bandwidth.  Scintillation variations are multiplicative and have a one-sided exponential probability distributino function that can yield occasional large-amplitude ``scintles'' that are several times the mean scintle amplitude of unity.

The spectral variations could in principle also include contributions from self noise in the source but to be significant, intrinsic fine structure in the burst would have to be on microsecond scales.

\subsection{Temporal, Energy, and Brightness Distributions of Bursts}
\label{sec:disn}

The burst rate for \frb\ varied dramatically throughout the 2016 observing campaign. In the early-2016 campaign, we observed for 30 hours at 3~GHz and no bursts were detected. In the late-2016 observing campaign, we observed for 27 hours at 3~GHz and detected nine bursts. Overall, the data quality is uniform and high, so the inhomogeneous burst distribution shows that the burst rate was not uniform.

@@

% ** clean this up
The integrated burst flux density is calculated by integrating the burst spectral model (Table \ref{tab:spec}) in frequency and time. Some VLA burst spectra seem to be contained by the 2.5 to 3.5~GHz band and most of them seem to have Gaussian envelopes that are well modeled by the emission within that band. Assuming that the Gaussian shape defines the full emission window, the integrated 3~GHz flux density can be converted to a total energy with no further assumptions about the burst spectral properties as:

\begin{equation}
E_{\rm{int}} = 10^{-23} \rm{dt} (4\pi L_d^2) \rm{amplitude} 2.355 \sigma \rm{erg}
\end{equation}
\noindent where...

@@

Broadly, the range of energies shown in Figure \ref{fig:ed} is defined by the sensitivity of the telescope and the duration of the observing campaign. The VLA distribution shown represents the 27-hour, late-2016 campaign, which is longer than the single-dish campaigns presented here. However, since the VLA observations have a relatively coarse time resolution, it is not as sensitive as Arecibo and the GBT, so no bursts with energies less than $3\times10^{38}$~erg were detected. The rate upper limit (95\% confidence) from the early-2016 VLA campaign shows that even identical observing campaigns have different detection rates.

We modeled the differential energy distribution, $dN/d\log{E}$, again using a Poisson detection probability with a rate function $\lambda = A E^{\alpha}$. Rather than trying to estimate a completeness limit for each energy distribution, we assume an effective detection limit of 0.9 times the weakest burst detected; the best-fit slope is weakly dependent on this, but general conclusions are robust. We directly sampled the likelihood distribution to estimate a best slope of $\alpha_{\rm{VLA}}=-0.6^{+0.2}_{-0.3}$, $\alpha_{\rm{Arecibo}}=-0.8^{+0.3}_{-0.5}$, and $\alpha_{\rm{GBT}}=-0.8^{+0.4}_{-0.5}$ (68\% confidence interval). Expressed as a power law function in $dN/dE$, the slope index is approximately --1.7. We caution that propagation effects can potentially modulate the intrinsic flux density and significantly affect any interpretation about burst amplitudes.

@@

% ** jim does not like red spectrum. recast using new paper?

@@

\software{\emph{rtpipe}, \emph{realfast}, pwkit \citep{2017ascl.soft04001W}}
